Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-03 WSSSPE2_report/WSSSPE2_review.tex
Section 4: Add mini-summary from speaker.

>>>>

How open is open source? Open software needs a diverse, openly governed
community behind it, just as it needs open licensing and a public code
repository. To probe the level of governance within open source projects, we
suggest a contest to encourage individual developers to submit patches and pull
request to projects that are important to them. This simple mechanism will
expose several governance mechanisms, such as how easy it is for independent
developers to communicate with project leadership, how projects accept and
properly license third party contributions, and how projects make decisions such
as granting source tree write access.
